---
title: "useR! 2025"
format: html
toc: true
execute:
  warning: false
---

```{r}
#| label: load-packages
library(tidyverse)
library(scales)
library(ggwordcloud)
library(gt)
```

```{r}
#| label: load-data
program <- read_csv("data/program.csv")
```

```{r}
#| label: colors

# yellow
keynote_color <- "#FFD960"

# blue
blue <- "#2165B6"
tutorial_color <- paste0(blue, "80")
talk_color <- paste0(blue, "60")
lightning_talk_color <- paste0(blue, "20")
light_blue <- "#A0b9E2"

# grey
poster_color <- "#E2E6ED50"
dark_grey <- "#323232"

# green
green <- "#65B621"
virtual_talk_color <- paste0(green, "60")
virtual_lightning_talk_color <- paste0(green, "20")
light_green <- "#C0ED9B"
```

```{r}
#| label: helper-make-schedule
make_schedule <- function(x, color){
  
  fill_color <- paste0(color, "50")

  x |>
  gt(rowname_col = "time", groupname_col = "session") |>
  fmt_markdown(columns = c(info, speakers)) |>
  tab_style(
    style = list(
      cell_fill(color = fill_color), 
      cell_text(weight = "bold", size = "120%")
    ),
    cells_row_groups()
  ) |>
  cols_width(
    info ~ px(800),
    speakers ~ px(300)
  ) |>
  cols_align(align = "left", columns = everything()) |>
  cols_label(
    room = "Room",
    time = "Time",
    info = "Title, abstract, and more info",
    speakers = "Presenter(s)"
  ) |>
  tab_style(
    style = cell_text(weight = "bold"), 
    locations = cells_column_labels(everything())
  )
}
```

# Overview

## In-person program

### Counts

```{r}
#| label: valuebox-values-inperson
program_inperson <- program |> 
  filter(date != "2025-08-01") |>
  mutate(
    session_simplified = case_when(
      str_detect(session, "tutorial") ~ "Tutorial",
      str_detect(session, "Keynote") ~ "Keynote",
      session == "Poster" ~ "Poster",
      session == "Lightning" ~ "Lightning talk",
      .default = "Talk"
    ),
    .after = session ,
    session_simplified = fct_relevel(session_simplified, "Keynote", "Tutorial", "Talk", "Lightning talk", "Poster")
  )

program_inperson_counts <- program_inperson |>
  count(session_simplified)

program_inperson_counts
```

### Daily counts

```{r}
#| label: session-counts-per-day-inperson
session_counts_per_day_inperson_plot <- program_inperson |>
  count(date, session_simplified) |>
  mutate(
    date = case_when(
      date == "2025-08-08" ~ "Day 1 - August 8, 2025",
      date == "2025-08-09" ~ "Day 2 - August 9, 2025",
      date == "2025-08-10" ~ "Day 3 - August 10, 2025",
    )
  ) |>
  ggplot(aes(y = fct_rev(session_simplified), x = n, fill = session_simplified)) +
  geom_col(show.legend = FALSE, color = blue) +
  facet_wrap(~date, ncol = 3) +
  labs(x = NULL, y = NULL) +
  scale_fill_manual(
    values = c(
      "Keynote" = keynote_color,
      "Tutorial" = tutorial_color,
      "Talk" = talk_color,
      "Lightning talk" = lightning_talk_color,
      "Poster" = poster_color
    )
  ) +
  theme_minimal() +
  theme(
    panel.grid.major.y = element_blank(),
    strip.background = element_rect(fill = poster_color, color = "white")
  )

session_counts_per_day_inperson_plot
```

### Themes

```{r}
#| label: keyword-wordcloud-inperson
program_inperson_themes <- program_inperson |>
  separate_longer_delim(keywords, delim = ", ") |>
  mutate(keywords = str_trim(keywords)) |>
  filter(!is.na(keywords)) |>
  count(keywords, sort = TRUE) |>
  filter(n > 1) # instances of more than 1 appearance only

keyword_wordcloud_inperson_plot <- ggplot(program_inperson_themes, aes(label = keywords, size = n, color = n)) +
  geom_text_wordcloud_area(rm_outside = TRUE, seed = 123) +
  scale_size_area(max_size = 30) +
  theme_void()

keyword_wordcloud_inperson_plot +
  scale_color_gradient(low = light_blue, high = blue)
```

## Virtual program

### Counts

```{r}
#| label: valuebox-values-virtual
program_virtual <- program |> 
  filter(date == "2025-08-01")

program_virtual_counts <- program_virtual |>
  count(session)

program_virtual_counts
```

### Themes

```{r}
#| label: keyword-wordcloud-virtual
program_virtual_themes <- program_virtual |>
  separate_longer_delim(keywords, delim = ", ") |>
  mutate(keywords = str_trim(keywords)) |>
  filter(!is.na(keywords)) |>
  count(keywords, sort = TRUE) |>
  filter(n > 1)

keyword_wordcloud_virtual_plot <- ggplot(program_virtual_themes, aes(label = keywords, size = n, color = n)) +
  geom_text_wordcloud_area(rm_outside = TRUE, seed = 123) +
  scale_size_area(max_size = 50) +
  theme_minimal()

keyword_wordcloud_virtual_plot +
  scale_color_gradient(low = light_green, high = green)
```

# Schedule

Please note that all session times are listed below in EDT and the schedule is subject to change.

```{r}
#| label: split-days
virtual <- program |> filter(date == "2025-08-01") |> select(!c(date, keywords))
day_1   <- program |> filter(date == "2025-08-08") |> select(!c(date, keywords))
day_2   <- program |> filter(date == "2025-08-09") |> select(!c(date, keywords))
day_3   <- program |> filter(date == "2025-08-10") |> select(!c(date, keywords))
```

## Virtual - August 1, 2025

The following talks are virtual and will be streamed on YouTube Live.

```{r}
#| label: virtual-schedule
#| html-table-processing: none

virtual |>
  make_schedule(color = green) |>
  cols_hide(columns = room)
```

## Day 1 - August 8, 2025

The following tutorials and posters will be presented in person at Duke University, Durham, NC.

```{r}
#| label: day1-schedule
#| html-table-processing: none
day_1_updated <- bind_rows(
  day_1 |> filter(session == "Morning tutorial"),
  day_1 |> filter(session == "Afternoon tutorial"),
  day_1 |> filter(session == "Keynote #1"),
  day_1 |> filter(session == "Poster")
) |>
  mutate(room = if_else(session == "Keynote #1", "Gross Hall 270", room))

make_schedule(day_1_updated, color = blue)
```

## Day 2 - August 9, 2025

The following tutorials and posters will be presented in person at Duke University, Durham, NC.

```{r}
#| label: day2-schedule
#| html-table-processing: none
make_schedule(day_2, color = blue)
```

## Day 3 - August 10, 2025

The following tutorials and posters will be presented in person at Duke University, Durham, NC.

```{r}
#| label: day3-schedule
#| html-table-processing: none
make_schedule(day_3, color = blue)
```
